Fermi and eROSITA bubbles: A proof-of-concept study

### 2021-12-19 paper.tex
update

  \subsection{The Galactic Model}
  As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
  by an external plane-parallel potential that is symmetric about the mid-plane $z=0$\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

@@

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  we can write the steady-state gaseous density distributions of disk and atmosphere\
  that are in pressure equilibrium and\
  confined in the total potential, $\Phi_{\text{total}}$, as\
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is a proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and atmosphere on the mid-plane $z=0$.

@@

@@

  confined by an external dark halo potential.

  The adopted parameters for are

  %We use three components (1) cold ISM disk (2) hot gas ambient (3) stellar disk\
  %to locally mimic the environment near the GC (i.e. no galactic rotation).\

  %The density distributions of ISM disk and hot gas ambient are derived from\
  %hydrostatic equilibrium within the fixed external potential.

  %We use the potential of isothermal slab, symmetric about $z=0$, and\
  %supported by gas pressure and by its own self-gravity,\
  %to mimic the realistic potential of Galactic bulge.

>>>>

  \subsection{The Galactic and Disk Models}
  As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
  by an external plane-parallel potential that is symmetric about the mid-plane $z=0$\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

@@

  With the help of the isothermal and hydrostatic equilibrium conditions,\
  we can write the steady-state gaseous density distributions of disk and the Galactic atmosphere\
  that are in pressure equilibrium and\
  confined in the total potential, $\Phi_{\text{total}}$, as\
  \begin{equation}
     \rho(z)=
     \begin{cases}
     \displaystyle\rho_{\text{disk}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{disk}}/m_{\text{p}}}\right] & \text{, if $|z| < z_{0}$}\\
     \\
     \displaystyle\rho_{\text{atmp}}^{\text{peak}}
     \exp\left[-\frac{\Phi_{\text{total}}(z)}{k_{B}T_{\text{atmp}}/m_{\text{p}}}\right] & \text{, otherwise,}
     \end{cases}
  \end{equation}
  where $m_{\text{p}}$ is a proton mass,\
  $T_{\text{disk}}$ and $T_{\text{atmp}}$ is the temperature of the disk and the atmosphere,\
  $\rho_{\text{disk}}^{\text{peak}}$ and $\rho_{\text{atmp}}^{\text{peak}}$ is the peak mass density\
  of the disk and atmosphere on the mid-plane $z=0$.

@@

  \Cref{density-profile} shows the initial density profile of hot halo for the simulation presented here.\

  \begin{figure*}[h]
    \subfigure[The initial gaseous density profile along z-axis] % caption
    {
      \includegraphics[width=0.4\linewidth]{figures/fig__density-profile.png}
      \label{density-profile}
    }
  \caption{Captions}
  \end{figure*}

@@

  \subsubsection{The clumpy, and warm/cold ISM disk}

  A crucial ingredient in the simulations is the clumpy ISM disk,\
  in which the temperature ranging from
